%-----WORK EXPERIENCE----------------------------------------------------------
\begin{comment}
  try to briefly explain what you did and why it is relevant to the position you
  are seeking
  \end{comment}
  
  \section{Work Experience}
   \vspace{0.8ex}
    \CVSubHeadingListStart
      \CVSubheading
        {Software Engineer}{July 2025 -- February 2026}
        {Huex GmbH \textbullet\ \faEnvelope\ \href{https://drive.google.com/drive/folders/13wautb-BFqIhc5TrnweBb3byhLBYIYIr?usp=drive_link}{\textcolor{gray}{Service Letter}} \textbullet\ \faTasks\ \href{https://drive.google.com/drive/folders/1PLMBp_KXhIdOvCCbuFgY43aa29-ksbIc?usp=drive_link}{\textcolor{gray}{Tasks}}}{Germany, Remote}
         \vspace{0.5ex}
        \CVItemListStart
          \CVItem{Worked as a Full-Stack Developer and System Designer on Talport, an AI-powered talent intelligence platform, managing Google Cloud VM instances and ensuring high availability, scalability, and security, and designed an AI-driven interview platform using advanced context engineering principles in the HR \& Talent Intelligence domain.}
          \CVItem{Researched and currently developing an agentic AI approach to build an automated, self-improving interview question bank system and integrated AI-powered question banks directly into live interviews to dynamically generate role- and skill-specific interview flows.}
          \CVItem{Integrated Google Gemini models to conduct AI-powered interviews with deep contextual understanding and designed intelligent question-and-answer evaluation mechanisms to accurately assess candidate responses.}
          \CVItem{Designed and developed interview scoring, analytics, and candidate ranking systems to enable data-driven hiring decisions.}
          \CVItem{Containerized both frontend and backend applications using Docker, ensuring consistency across development, testing, and production environments, and designed automated CI/CD pipelines using GitHub Actions with separate environments for testing and production, branching strategies, and deployments to separate Google Cloud VMs.}
          \CVItem{Integrated Caddy as a reverse proxy for automatic SSL certificate generation, HTTPS enforcement, and domain configuration, ensuring secure communication and improved SEO.}
          \CVItem{Refactored the entire frontend application using Clean Architecture principles in React, focusing on separation of concerns, reusable modular components, maintainable folder structure, and improved state management, and restructured the backend using layered architecture with FastAPI, clearly separating API layer, business logic, data access layer, and infrastructure.}
          \CVItem{Integrated Swagger (OpenAPI) into the backend to provide interactive API documentation and implemented end-to-end encryption and security mechanisms to secure candidate information, prevent unauthorized data scraping, and enforce controlled access to sensitive endpoints.}
          \CVItem{Implemented k6 performance and load testing for backend API endpoints to validate scalability and reliability, and maintained environment-specific configurations using GitHub encrypted variables and secrets for secure deployments.}
          \CVItem{Integrated Google Calendar APIs to automate interview scheduling and event management, and designed a self-hosted internal meeting solution using Jitsi for secure video conferencing.}
          \CVItem{Designed and implemented automated database and Supabase Edge Function migration workflows, enabling seamless SQL schema migrations and Edge Function deployments on project startup, and authored comprehensive technical documentation for features and system architecture using Confluence.}
          \CVItem{Mentored junior developers through code reviews, architectural discussions, and best-practice guidance.}
        \CVItemListEnd
        \techlist{Technologies \& Design Patterns}{%
          \techcard{System Design} \techcard{Clean Architecture (Frontend)} \techcard{Layered Architecture (Backend)} \techcard{Repository Pattern} \techcard{Context Engineering} \techcard{Agentic AI} \techcard{RAG} \techcard{Google Cloud VM} \techcard{Gemini AI} \techcard{React} \techcard{FastAPI} \techcard{Docker} \techcard{GitHub Actions} \techcard{Caddy} \techcard{Swagger} \techcard{Google Calendar API} \techcard{Supabase} \techcard{Jitsi} \techcard{REST APIs} \techcard{k6} \techcard{Figma}%
        }\\
         \vspace{1.8ex}
        {\color{gray!40}\dotfill} % <-- very light dotted line
      \CVSubheading
        {Software Engineer}{January 2016 -- July 2016}
        {Drifting Desk LLC \textbullet\ \faEnvelope\ \href{https://drive.google.com/drive/folders/1ztfrTaknZsK9tdcHMfntQGt7EMU7RXOP?usp=sharing}{\textcolor{gray}{Service Letter}} \textbullet\ \faTasks\ \href{https://drive.google.com/drive/folders/1VxwTauBBuxH21_G90LczULGxi8xHStZ0?usp=sharing}{\textcolor{gray}{Tasks}}}{USA, Remote}\\
      \vspace{0.5ex}
        \CVItemListStart
          \CVItem{Worked as a .NET Core backend developer on an AI-driven multi-tenant hotel management platform, developed booking optimization and competitor intelligence features for a European client, and integrated cutting-edge AI, real-time data analysis, and automation to help hotel chains make smarter decisions.}
          \CVItem{Developed scalable CRUD modules with Kafka integration for seamless internal microservice communication and implemented Request Response and Fire-and-forget patterns for external system communication.}
          \CVItem{Built a centralized Anti-XSS middleware and developed a unified access management mechanism to enforce security across all frontend and backend APIs.}
          \CVItem{Researched Hangfire job strategies and designed and implemented a similar job execution strategy using .NET Worker Services for recurring tasks and large-scale data imports.}
          \CVItem{Implemented .NET Server-Sent Events (SSE) for real-time chart updates and live table updates.}
          \CVItem{Conducted K6 performance tests and comprehensive performance testing to validate system reliability and scalability.}
          \CVItem{Integrated Keycloak REST APIs for secure, multi-tenant authentication and implemented user management using Keycloak integration.}
          \CVItem{Researched and implemented Kafka consumer parallelism to enhance real-time data processing capabilities and developed custom pagination logic for efficient rendering of large datasets.}
          \CVItem{Configured Bitbucket Pipelines to dynamically read Helm chart values, enabled environment-specific deployments through automated pipeline configuration, and integrated security vulnerability scans into the pipeline to improve CI/CD security compliance.}
          \CVItem{Mentored junior developers on architecture, coding standards, and secure development practices.}
        \CVItemListEnd
        \techlist{Technologies \& Design Patterns}{%
          \techcard{.NET Core} \techcard{Microservices} \techcard{Docker} \techcard{Kubernetes} \techcard{Keycloak} \techcard{REST APIs} \techcard{Kafka} \techcard{MongoDB} \techcard{Redis} \techcard{MinIO} \techcard{Bitbucket} \techcard{JWT} \techcard{xUnit}%
        }\\
         \vspace{1.8ex}
       {\color{gray!40}\dotfill} % <-- very light dotted line
      \CVSubheading
        {Associate Software Engineer}{August 2023 -- July 2024}
        {ICP Technologies (Pvt.) Ltd \textbullet\ \faEnvelope\ \href{https://drive.google.com/drive/folders/1ZWdbhnBKfIoKxHMfjuH5MgZWeQM4xrZj?usp=drive_link}{\textcolor{gray}{Service Letter}} \textbullet\ \faTasks\ \href{https://drive.google.com/drive/folders/1M0M7b3Y9MVta_XvFu4bKrcN_AYEQL2Ys}{\textcolor{gray}{Tasks}}}{Sri Jayewardenepura Kotte, Sri Lanka}\\
       \vspace{2.8ex}
        \textbf{Accounting Software - Enterprise Management Domain (4 Months)}
        \begin{itemize}[leftmargin=0.8cm]
          \item Designed and setup backend core architecture, committed the initial project to a private Azure repository, updated wiki pages, and implemented a centralized audit \& request logs mechanism using Spring AOP, Filters, and handler interceptors.
          \item Developed initial RESTful endpoints for the backend services, wrote unit test cases to ensure high code quality, and introduced dynamic queries to enhance the flexibility and efficiency of the data access layer.
          \item Mentored junior developers to enhance their skills and knowledge.
        \end{itemize}
        \techlist{Technologies \& Design Patterns}{%
          \techcard{Modular Architecture} \techcard{Spring Boot} \techcard{JUnit} \techcard{JaCoCo} \techcard{MySQL} \techcard{JPA Specification} \techcard{Docker} \techcard{Keycloak} \techcard{JWT} \techcard{Azure DevOps}%
        } \\
        \vspace{1.2ex}
        \textbf{Banking Application - FinTech Domain (7+ Months)}
        \begin{itemize}[leftmargin=0.8cm]
          \item Primarily worked as a .NET Core backend developer for Jack Henry, a leading FinTech solution provider in the USA.
          \item Designed and developed an enhanced \& centralized Transactional Outbox pattern to address message loss issues from the queues, and implemented retention background workers to purge outbox tables according to defined policies and retry logic for failed messages and payments using .NET Core background workers.
          \item Conducted various testing methodologies, including unit, integration, and performance testing, and resolved production bugs.
        \end{itemize}
        \techlist{Technologies \& Design Patterns}{%
          \techcard{CQRS} \techcard{DDD} \techcard{Microservices} \techcard{Clean Architecture} \techcard{C\#} \techcard{.NET Core} \techcard{RabbitMQ} \techcard{MassTransit} \techcard{MS SQL} \techcard{Dapper ORM} \techcard{JMeter} \techcard{MediatR} \techcard{Azure DevOps} \techcard{Datadog}%
        }\\
        \vspace{1.8ex}
        {\color{gray!40}\dotfill} % <-- very light dotted line
      \CVSubheading
        {Trainee Software Engineer}{February 2022 -- August 2022}
        {Mitra Innovation (Pvt) Ltd \textbullet\ \faEnvelope\ \href{https://drive.google.com/file/d/1HddEasuatcOICgqyft0xxuywZ6DnI9_B/view}{\textcolor{gray}{Service Letter}} \textbullet\ \faTasks\ \href{https://drive.google.com/drive/folders/1NjvOFHov_gu9cA6KCHObYDRdC1fOP688?usp=sharing}{\textcolor{gray}{Tasks}}}{Moratuwa, Sri Lanka}\\
        \vspace{2.8ex}
        \textbf{Triton by Dygisec - Cloud Security Domain (4 Months)}
        \begin{itemize}[leftmargin=0.8cm]
          \item Worked as a Golang backend developer, developing APIs, building ETL pipelines using AWS Lambda to PostgreSQL RDS, and creating API endpoints for compliance dashboard service.
          \item Documented all REST API endpoints using Swagger UI across all services in the project and researched and built OpenID Connect \& OAuth2.0 plugin for Kong Gateway.
          \item Collaborated on filling compliance data into Google Sheets with 11 tables, investigated Triton Confluence pages, and worked with compliance repositories: AWS CIS v1.2.0, AWS Best Practice FW, and PCI DSS 3.2.1.
          \item Built a Golang CSV file reader program to automate manual data.go file creation from policy compliance Excel sheets.
          \item Modified Entity Relationship Diagram (ERD) for Compliance and rules repository according to principal architect's feedback, and modified data seeder after database structure changes, verifying data seeding using K9s logs and DBeaver.
          \item Created Google Sheet documenting 250+ AWS managed config rules, designed and implemented ETL pipeline to read files from S3 bucket and load into AWS RDS PostgreSQL database, and automated ETL deployment process using AWS CloudFormation service with YAML configuration.
        \end{itemize}
        \techlist{Technologies \& Design Patterns}{%
          \techcard{Microservices} \techcard{Go} \techcard{Kong Gateway} \techcard{Helm} \techcard{Swagger} \techcard{Kubernetes} \techcard{Docker} \techcard{GORM} \techcard{AWS} \techcard{Agile Development} \techcard{JIRA} \techcard{Slack}%
        } \\
        \vspace{1.2ex}
        \textbf{ATS - HR \& Recruitment Domain (2 Months)}
        \begin{itemize}[leftmargin=0.8cm]
          \item Created relational database and designed ER diagram for ATS by observing entities through PeopleHR sandbox environment, and developed scheduler to sync PeopleHR data with the proposed ATS application.
          \item Designed wireframes for ATS using Figma UX/UI design tool.
          \item Collaborated with all developers on applicant tracking system project tasks.
          \item Designed project timeline and Gantt chart using Jira project management tools.
        \end{itemize}
        \techlist{Technologies}{%
          \techcard{Lucidchart} \techcard{Figma} \techcard{Angular} \techcard{PeopleHR APIs}%
        }
    \CVSubHeadingListEnd
  